String Constraints with Regex-Counting and String-Length Solved Efficiently

### 2023-05-09 2023-1-19/sections/implementation.tex
benchmark

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,751 instances in the AutomatArk suite.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} include 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. Only 8,751 ones out of 19,979 instances contain occurrences of counting operators.

>>>>

\paragraph*{AutomatArk benchmark suite.}
The AutomatArk benchmark suite is adapted from the AutomatArk suite in \cite{z3str3re} by filtering out the string constraints that contain no occurrences of counting operators and adding the length constraint $|x| > 10$ (where $x$ is a string variable). There are 8,751 instances in the AutomatArk suite here.
Note that the original AutomatArk benchmark suite in \cite{z3str3re} includes 19,979 instances in total, which are conjunctions of regular membership queries and generated out of regular expressions from \cite{automatark}. 
%Only 8,751 ones that contain counting operators out of 19,979 instances.
